Where is the Context for Disambiguation? An Experimental Analysis.

### 2013-10-19 draft.tex
moved pdfs; clarification for context score generation task

\todo{Carol will generate one index per type of context. For each disambiguation, she will query all indexes, obtain a ``contextual score'' and output a TSV file with $\langle occId, correctUri, contextScore1, contextScore2, ..., contextScoreN\rangle$. First line of the TSV is the header with names of columns.}
\todo{Pablo will run the machine learning algorithms once provided the data.}

>>>>

\todo{Carol will generate one index per type of context. For each disambiguation example in an evaluation set, she will query eachof the indexes, obtain a ``contextual score'' for each of the N indexes and output a TSV file with $\langle occId, correctUri, contextScore1, contextScore2, ..., contextScoreN\rangle$. First line of the TSV is the header with names of columns.}
\todo{Pablo will run the machine learning algorithms once provided the data.}
